Browsing the Web of Factual Claims

### 2008-09-16 papers/web_of_ideas/web_of_ideas.tex
Part way through writing up user study stuff

\section{Iterative Evaluation}

Think link was developed using an iterative design process. During each iteration, we would talk to participants about the way they found and organized information on the web, and then perform a think aloud study where the participants would use the tool and tell us what they were thinking. After each iteration, we would study what we had learned from the participants and update our prototype accordingly. We went through a total of four iterations, with varying degrees of formality.

\subsection{Investigatory Study}

\subsection{Evaluation Study}

We performed two user studies. In the first study, we asked participants about how they found and organized information on the web, and performed a think aloud study where they used the tool and told us what they were thinking. The learnings from the first study.

In the first user study, we perf

showed the participants an early version of the Think Link interface

Think Link was developed using an iterative design process.

We performed two user studies. The aim of the first study was to determine

In the first of these studies, we recruited 12 paid subjects, aske

\subsection{Interaction Techniques}

The web has provided users with many pages that they can read.

1p:  
overview, 
motivation,
list of contributions,
(briefly) describe application,
(briefly) describe user studies,
describe results,

%\studyresult{The best way to find answcuters is social - by learning from friends who understand the topic}

>>>>

\section{Investigative Study}

We performed two ``think aloud'' studies to guide and evaluate the development of Think Link. The aim of the first study was to see how users normally browse the web and to see how they might try to use an initial prototype of Think Link to help them.

\subsection{Protocol for the First Study}

We recruited 12 paid participants. Five were female, seven were male. Their ages ranged from high school age to retired. Our intention was to recruit users who were not experts, but who regularly used the internet to find information. We recruited participants using a posting to the Craigslist~\cite{craigslist} classified adverts site. In our advert, we expressed an interest in people who use the internet to gather knowledge, rather than just for tasks such as email or shopping. We filtered participants based on their short answers to questions about how they found, organized, and shared information on the web.

\subsection{Study Protocol}

Study sessions took approximately 45 minutes. Participants were seated at a single-screen workstation with the Firefox browser, augmented with the Think Link plugin. We first demonstrated Think Link's interface, and then asked them to perform two tasks. In the first task, we asked them to use Think Link to gather information about a political topic that was of interest to them and currently in the news. For the second task, we asked them to browse the web in a way that would typically do so at home or at work, and see if they could use Think Link to help them do so.

In the second task, we wanted to leave users relatively unconstrained so that we could see how users might try to use a tool like this during their normal browsing, rather than how well they could accomplish a pre-set task that they might never attempt in normal life. For the first task, we constrained the task to an a topic for which we had already marked up a number of claims, to increase the likelyhood that users would encounter existing claims.

\subsection{Findings}

All the participants were able to create new snippets. Participants had little difficulty identifying interesting claims being made by web pages, selecting appropriate sections of text, and either picking existing claims that were appropriate, or writing appropriate new claims. Most ($9/12$) stated that they found it easy to create new snippets and associate them with claims.

In the initial interface, snippets were only highlighted when the margin was open. This confused some participants ($5/12$) who were surprised to not see their snippets highlighted when they created them. This led us to change the interface so that snippets were always highlighted.

In the initial interface, the button to open the margin was on the toolbar, next to the ``new snippet'' button, rather than

Two participants initially had dificulty summarising text with a claim that the text was actually making, rather than an claim it was associated with.

Many ($7/12$) participants also expressed a desire to organize snippets and claims during their session. Of these seven, we noticed that four would alternate between creating new snippets and organizing their claims in the claim browser (Section~\ref{claimbrowser}). With each new claim, users would create relationships between existing claims.

\subsection{The Prototype Interface}

Participants were shown an earlier interface than that described in Section~\ref{interface}.

\begin{figure}[ht]
	\includegraphics[scale=0.35]{../screenshots/snippetdialog_sm.jpg}
	\caption{First Prototype Snippet Creation Dialog}
	\label{oldsnippetbox}
\end{figure}

\subsection{Successes}

All the participants were able to create new snippets, succeeding in identifying appropriate sections of text that should be marked, and picking out either an appropriate existing claim, or creating a new claims that accurately summarized the snippet. Two participants initially had difficulty in correctly summarizing text with a claim that the text was actually making, but they eventually got used to it.

Many ($7/12$) participants also expressed a desire to organize snippets and claims during their session. Of these seven, we noticed that four would alternate between creating new snippets and organizing their claims in the claim browser (Section~\ref{claimbrowser}). With each new claim, users would create relationships between existing claims.

Most ($10/12$) either reused a topic that they had created themselves or that we had previously created. While the level of social activity was undoubtedly limited by the relatively small number of claims available in our database and the wide range of topics participants read about, three of the six people who browsed points in the

\subsection{Observations Motivating Design Changes}

\subsection{Browsing Claims}

\subsection{Creating Snippets}

\section{Evaluation Study}

The purpose of the second study was to evaluate whether the interface changes we had made in reaction to the first study had made the tool usable.

\subsection{Recruitment}

We recruited 6 paid participants. Four were female and two were male. Although we recruited participants using the same advert as the first study, the timing of our second advert around the beginning of the semester meant that five of the participants were students. Since the second group was different demographically to the first group, it is not possible to make a direct comparison between their behaviours. However we were still able to make interesting observations about how users used the new interface.

\subsection{Study Protocol}

For the second study, we changed the task to focus on how easy users found it to use the interface, rather than on how they might apply it to their normal browsing. We told users nothing about how to use the tool. Instead, we just gave them a brief introduction to what our tool was for, and then asked them to attempt two tasks. The first task was to look at a selection of web pages that already had highlights and tell them to explore the interface. The second task was to identify claims on a page that had not been marked up and connect them appropriately to existing claims.
